Weak lensing Hierarchy Bayesian Inference

### 2013-02-13 write-up.tex
Update write-up.tex

Several beysian or likelihood approaches towards shear measurement
like lensfit(L. Miller,T. D. Kitching et al,2007;T.D. Kitching, L.
Miller et al 2008 ) im2shape(Bridle,) im3shape(Joe Zuntz, et al,arxive2013)
have bean make recently.{[}im3shape fitted different models on galaxies
image and used a max-likelihood method to determin the model parameters,and
then obtain the galaxy's ellipticity.{]}{[}lensfit proposed a modelfitting
approach in the galaxy shape measurement and evaluated how shear sensitivity
should be calculated based on posterior distribution of galaxies shape.{]}
However these methods mostly focus on the shape measurement of a single
galaxy.Given an telescope that has perfect measurement on galaxies'
shape their shear estimation method is no different thatn traditional
averaging method.

>>>>

Several beysian or likelihood approaches towards shear measurement
like lensfit(L. Miller,T. D. Kitching et al,2007;T.D. Kitching, L.
Miller et al 2008 ) im2shape(Bridle,) im3shape(Joe Zuntz, et al,arxive2013)
have bean make recently.{[}im3shape fitted different models on galaxies
image and used a max-likelihood method to determin the model parameters,and
then obtain the galaxy's ellipticity.{]}{[}lensfit proposed a modelfitting
approach in the galaxy shape measurement and evaluated how shear sensitivity
should be calculated based on posterior distribution of galaxies shape.{]}
However these methods mostly focus on the shape measurement of a single
galaxy.Given an telescope that has perfect measurement on galaxies'
shape their shear estimation method has no difference with traditional
average method.
